\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{hyperref}
\usepackage{scimisc-cv}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Shiva Reddy Kokilathota Jagirdar}
\cvpersonalinfo{
\textbf{shiva.reddy.kj@gmail.com}\cvinfosep
\textbf{+1 (312) 678-9776} \cvinfosep
\href{https://github.com/shiva-reddy}{\textbf{github/shiva-reddy}} \cvinfosep
\href{https://www.linkedin.com/in/shiva-reddy-kj/}{\textbf{linkedIn/shiva-reddy-kj}}
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo
\section{OBJECTIVE}
\section{Education}
\cvsubsection{\normalfont{}\textbf{University of Illinois at Chicago (UIC)}, Chicago, IL }[\normalfont{}Aug 2019 - Present \textbf{(Anticipated May-2021)}]
[\normalfont{}Master of Science in \textbf{Computer Science. }][GPA: 4/4]
\vspace{0.1cm}
\cvsubsection{\normalfont{}\textbf{Amrita school of engineering}, Bangalore, India}[\normalfont{}Aug 2012 - Jun 2016]
[\normalfont{}Bachelor of Technology in \textbf{Computer Science}][GPA: 8.46/10]
\vspace{0.5cm}
\section{Technical Skills}
\begin{itemize}
\item \textbf{Programming Languages:} Java, Javascript, Python, C++ and Golang.
\item \textbf{Platforms, web-development and databases:} Java EE,HTML/CSS, Android, Django, nodejs, Reactjs, MYSQL, MongoDB and DynamoDB
\item \textbf{Devops and deployment:} Heroku, Google cloud platform, Firebase, AWS services (S3, API Gateway, Batch, Lambda, VPC and CloudFormation)
\end{itemize}
 
\vspace{0.5cm}
\section{Professional Experience}

\cvsubsection{Amazon AWS, CodeGuru Reviewer}[\normalfont{}Seattle (Remote)]
[Software development Engineer intern - Full stack][\normalfont{} June 2020 - August 2020]
\vspace{0.25cm}
\begin{itemize}
\item Built an end-to-end service that allows users to tag Machine learning datapoints with properties, and generate custom ML datasets based 
on data point properties rules. Involved in the full development life cycle, from initial design and prototyping, to development, testing and release. 
Led discussions with stakeholders to discuss the overall product vision.
\item The backend \textbf{REST API} service was built using \textbf{AWS Lambda (Java)}, \textbf{API Gateway} and \textbf{DynamoDB}.
\item The UI portal was built using \textbf{ReactJS} for page rendering with Polaris(internal) stylekit for styling, and \textbf{AWS Lambda} 
and \textbf{AWS S3} for serving UI content.


\end{itemize}

\cvsubsection{Chargebee}[\normalfont{}Chennai, India][Software engineer - Full stack][\normalfont{} Jan 2016 - May 2019]
\vspace{0.25cm}
\begin{itemize}
\item Built services for the  \emph{Integration} and \emph{E-commerce} teams using \textbf{Java EE} and \textbf{MYSQL} databases, 
on top of internal web frameworks.
\item Responsible for collaborating with product and design teams to build features 
and software modules for the subscription billing platform Chargebee. Designed, developed and maintained :-
\begin{itemize}
\item The recurring delivery management module for the product. The module is a key market differentiator for the product and is currently being used by Chargebee’s customers to 
service \emph{thousands of deliveries} every day.
\item The revenue recognition reporting system in a team of 3, to automate the revenue recognition workflow for 
Chargebee’s customers.
\item An internal \textbf{REST API} based integration framework to integrate Chargebee to other web apps. Also used the framework to integrate 
Chargebee to accounting platform Xero. The framework has been used extensively by multiple teams to support over 10 other core integrations.
\end{itemize}
\end{itemize}

\vspace{0.5cm}
\section{Projects}

 \cvsubsection{\normalfont{}\textbf{LoopedIn}
 \href{https://github.com/LoopedIn/loopedin-web}{\em{github.com/LoopedIn/loopedin-web}}}[\normalfont{}Feb 2020 - May 2020]
\begin{itemize}
    \item A chat-focused social networking platform built using \textbf{ReactJS} for UI, \textbf{Redux} for client state management, 
    \textbf{MongoDB} as backing store, \textbf{Express + NodeJS} for backend server and \textbf{Firebase} for Authentication. 
    
    \item  Used \textbf{docker} containers to setup \emph{continuous development} and automatically deploy the service on the \textbf{Google cloud platform} stack. 
    \emph{Continuous integration} pipeline was implemented to run unit tests using \textbf{Github Actions}. 
   
\end{itemize} 

 \cvsubsection{\normalfont{}\textbf{ARify} \href{https://github.com/shiva-reddy-uic/arify-android-client}{\em{github.com/shiva-reddy-uic/arify-android-client}}}[\normalfont{}November 2019]
\begin{itemize}
    \item Developed an AR \textbf{Android} app which lets the user build dynamic \textbf{Augmented Reality} workflows. 
    The app uses \textbf{Viro ARCore} for rendering 3D objects on image detection. 
    The app's UI follows the latest design principles of material design.
    \item Developed a \textbf{Django (Python)} web server deployed on \textbf{Heroku} which lets the user upload a 3D object and allow them to link it to the image.
     The server also exposes a \textbf{REST} API, to be used by the android app. Used \textbf{sqlite-db} 
     for data storage and \textbf{Amazon S3} web service for file storage.
\end{itemize} 

 \cvsubsection{\normalfont{} \textbf{Stackoverflow  tag prediction}}[\normalfont{}November 2019]
\begin{itemize}
    \item Worked in a team to build a machine learning classifier (\textbf{Python}, \textbf{Pytorch}) to predict tags for 
    stackoverflow questions using datasets from Kaggle. Logistic regression, SVM and Neural network classifiers were used.
\end{itemize} 

 \cvsubsection{\normalfont{}\textbf{Mix network implementations}
 \href{https://github.com/nkprince007/mix-networks}{\em{github.com/nkprince007/mix-networks}}}[\normalfont{}Feb 2020 - April 2020]
\begin{itemize}
    \item Developed a mixed network proxy server implementation for \textbf{GoLang} which uses several mixing strategies 
    to randomize the order of requests in a TOR network and defends the privacy of the network when under attack.
\end{itemize} 

\end{document}

